### 2016-11-17 methodsPaper/tex/results.tex

>>>>

We report total change (averted or increased) in diability adjusted
life years (DALYs) as an estimate of dissease burden change with
alternative scenarios.

To estimate DALYs we use a methodology adopted from previous US
implementations of ITHIM which scale Global Budern of Disease
Estimates for the US to smaller populations using mortality rate
ratios \cite{maizlish2013}. Age, sex, and casuse specific mortalities
were obtained form the CDC WONDER database for US metro counties for
the years 2010-2014. Cells with less than 10 deaths were imputed using
R's random integer generator.
